### 2018-05-11 submission/manuscript.Rmd
remove old fig s1 from text

**Figure S1: HiFi DNA Polymerase Sequence Error Prevalence in Mock Samples.** A) Sequence error prevalence before the merger of sequences with pre.cluster and the removal of chimeras with VSEARCH. B) Sequence error prevalence before the removal of chimeras with VSEARCH. C) Full pipeline. The error bars represent the 75% interquartile range of the median.

**Figure S2: HiFi DNA Polymerase Nucleotide Subsitutions in Mock Samples.**

>>>>

**Figure S1: HiFi DNA Polymerase Nucleotide Subsitutions in Mock Samples.**

### 2018-05-11 submission/manuscript.tex
remove old fig s1 from text

\textbf{\emph{Statistical Analysis:}} All analysis was done with the R
(v 3.4.3) software package (R Core Team, 2017). Data transformation and
graphing was completed using the tidyverse package (v 1.2.1) and colors
selected using the viridis package (v 0.4.1) (Garnier, 2017; Wickham,
2017). Differences in the total number of OTUs were analyzed using an
ANOVA with a tukey post-hoc test. For the fecal samples the data was
normalized to each individual by cycle number to account for the
biological variation between people. Bray-Curtis distance matrices were
generated using mothur after 100 sub-samplings at 1000, 5000, 10000, and
15000 sequence depth. The distance matrix data was analyzed using
PERMANOVA with the vegan package (v 2.4.5) (Oksanen et al., 2017) and
Kruskal-Wallis tests within R. For both error and chimera analysis,
samples were tested using Kruskal-Wallis with a Dunns post-hoc test.
Where applicable correction for multiple comparison utilized the
Benjamini-Hochberg method (Benjamini \& Hochberg, 1995).

@@

\textbf{Figure S1: HiFi DNA Polymerase Sequence Error Prevalence in Mock
Samples.} A) Sequence error prevalence before the merger of sequences
with pre.cluster and the removal of chimeras with VSEARCH. B) Sequence
error prevalence before the removal of chimeras with VSEARCH. C) Full
pipeline. The error bars represent the 75\% interquartile range of the
median.

\textbf{Figure S2: HiFi DNA Polymerase Nucleotide Subsitutions in Mock
Samples.}

>>>>

\textbf{\emph{Statistical Analysis:}} All analysis was done with the R
(v 3.4.4) software package (R Core Team, 2017). Data transformation and
graphing was completed using the tidyverse package (v 1.2.1) and colors
selected using the viridis package (v 0.4.1) (Garnier, 2017; Wickham,
2017). Differences in the total number of OTUs were analyzed using an
ANOVA with a tukey post-hoc test. For the fecal samples the data was
normalized to each individual by cycle number to account for the
biological variation between people. Bray-Curtis distance matrices were
generated using mothur after 100 sub-samplings at 1000, 5000, 10000, and
15000 sequence depth. The distance matrix data was analyzed using
PERMANOVA with the vegan package (v 2.4.5) (Oksanen et al., 2017) and
Kruskal-Wallis tests within R. For both error and chimera analysis,
samples were tested using Kruskal-Wallis with a Dunns post-hoc test.
Where applicable correction for multiple comparison utilized the
Benjamini-Hochberg method (Benjamini \& Hochberg, 1995).

@@

\textbf{Figure S1: HiFi DNA Polymerase Nucleotide Subsitutions in Mock
Samples.}
